---
title: 'Presentation template'
subtitle: 'Subtitle'
date: '2023-03-05'
# More about date formats: https://quarto.org/docs/reference/dates.html#using-a-date-style
date-format: long
author: 'Some author'
format: 
  revealjs:
    # self-contained: true
#    smaller: true
    chalkboard: true
    theme: solarized
# More about themes: https://quarto.org/docs/presentations/revealjs/themes.html
bibliography: bibliography.bib
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(dpi = 300,
                      echo = FALSE,
                      warning = FALSE,
                      cache = FALSE,
                      fig.width = 5,
                      fig.height = 3,
                      out.width = '100%')

library('tidyverse') 
theme_set(theme_bw())
dat <- tibble(x = 0:100,
              y = runif(101))
gg <- dat %>% ggplot(aes(x, y)) + geom_point()
```

## Introduction
*   First bullet point
*   Second bullet point
    + Subbullet 1
    + Subbullet 2
        - Subsubbullet 1
* They showed something [@lavinder_boosted_2022]

## Single plot without text
```{r}
#| fig-align: center
gg
```

## Fixed aspect ratio
```{r}
#| fig-align: center
gg + theme(aspect.ratio = 1)
```

## Single plot with bullets underneath
```{r}
#| fig-align: center
#| fig-width: 2.5
#| fig-height: 2.5

 # increase fig-width to get a wider figure
gg
```
* Bullet 1 - try to use not more than two bullets
* Otherwise the figure will shrink

## Single plot with bullets aside
::: columns
::: {.column width="50%"}
* Bullet 1 
* Bullet 2
:::
::: {.column width="50%"}
```{r}
#| fig-align: center
#| fig-width: 3
gg
```
:::
:::

## The other way round
::: columns
::: {.column width="50%"}
```{r}
#| fig-align: center
#| fig-width: 3
gg
```
:::
::: {.column width="50%"}
* Bullet 1 
* Bullet 2
:::
:::



## References